Exploring the Role of Small Molecules in Biological Systems Using Network Approaches

### 2015-01-19 paper.tex
Getting started ....

\begin{document}
\title{Exploring the Role of Small Molecules in Biological Systems Using Network Approaches}
\author{Saurav Das$^\dagger$ and Rajarshi Guha$^\ddagger$\\
$^\dagger$Your Address \\
$^\ddagger$National Center for Advancing Translational Science \\ 9800 Medical Center Drive  Rockville, MD 20850}
\date{}

>>>>

\begin{document}
\title{Exploring the Role of Small Molecules in Biological Systems Using Network Approaches}
\author{Sourav Das$^\dagger$ and Rajarshi Guha$^\ddagger$\\
$^\dagger$St. Jude Children's Research Hospital \\ 262 Danny Thomas Place, Memphis, TN 38105 \\
$^\ddagger$National Center for Advancing Translational Science \\ 9800 Medical Center Drive  Rockville, MD 20850}
\date{}
